A thesis draft

### 2018-10-26 res/sections/10-ProjectAnalysis.tex
Fix English

\subsubsection{Harbor}
Started as a VNFM (Virtual Network Function Virtualization Manager) to offer 
a bridge for Openbaton to interact with Kubernetes, during the project it has 
been expanded to become a complete replacement of the original product, adding 
the possibility to manage Network Services and to update the routing tables 
contained in the Roulette Controller (the tool description can be found below
in~\ref{chap:prjan:sec:tech:sub:SFC:sub:roulette}). Harbor doesn't have a web 
interface, but it has a RESTful API that allow users to interact with him 
using CRUD operations. It offers functionalities similar to Openbaton: 
possibility to upload VNF definitions (basically, Kuberentes YAML deployments), 
and possibility to upload NS definitions. When an NS is saved, a consistency 
check is performed to assure that alle the VNF are already present in Harbor. 
Similarly to Openbaton an NS is deployed, all the associated VNFs are deployed 
with it, making the whole operation atomic from the user point-of-view. 
What Openbaton doesn't do is a smart resource utilization: Harbor, in fact, 
during NS is deletion, it checks if any related VNF remains orphan (which means 
without any NS using it). In that case the VNF will enter in a state of 
pruning: after five minutes, if the VNF has not be reutilized by another NS it 
will be deleted. This mechanism assure faster deployments in environments where 
NSs are continuously launched and deleted.

@@

\paragraph{Docker Swarm} Introduced in ??\todo{Find Docker Swarm date of
birth}, Docker Swarm allows multiple Docker nodes to cluster together and be
seen as one logical unit. This layer completely makes the underlying
infrastructure transparent: data management, as network one, are totaly managed
by Docker. Recently, Docker-compose support has been introduced, making this
one-node tool available for clustered systems. At the end of the day, on one
hand Docker Swarm provides an easy way to set up a cluster system with all the
tools configured out-of-the-box, without the necessity to set networking
configurations or installing ad-hoc storage solutions. On the other hand,
though, it doesn't have all the personalization options that Kuberentes offers,
thus making the product less flexible. This foundamental characteristic,
although, makes the two solutions have different use cases leading to different
market needs. \todo{Add Docker Swarm}

\paragraph{Docker-compose} As briefly discussed above, Docker-compose is a tool
that allows services orchestration. It automates most of the tasks that should
be performed by hand when launching one or multiple docker containers. It's
particulary useful when more continers have to interact together,
because\todo{Write down docker-compose functionalities and describe the product
  a little bit} all the services rules are described in a simple YAML file. With
the birth of Docker Swarm, work has started to port this tool to the Swarm
framework. At the time of this writing, the procedure to port a Docker-compose
configuration in Docker Swarm is still not completely transparent, and it
requires a sort of compilation, where Docker-compose bundles all the necessaries
resources into a binary file that Docker Swarm will use to allocate the
necessary resources.

>>>>

\subsubsection{Harbor}
Started as a VNFM (Virtual Network Function Virtualization Manager) to offer a
bridge for Openbaton to interact with Kubernetes, during the project it has been
expanded to become a complete replacement of the original product, adding the
possibility to manage Network Services and to update the routing tables
contained in the Roulette Controller (the tool description can be found below
in~\ref{chap:prjan:sec:tech:sub:SFC:sub:roulette}). Harbor doesn't have a web
interface, but it has a RESTful API that allow users to interact with it using
CRUD operations. It offers functionalities similar to Openbaton: possibility to
save and retrieve VNF and NS definitions (basically, Kuberentes YAML
deployments). When an NS is saved, a consistency check is performed to assure
that all the VNFs have already been defined in Harbor. On an NS deployment, with
a mechanism similar to the Openbaton one, all the associated VNFs are set up
too, making the whole operation of launching a NS atomic from the user
point-of-view. What Openbaton doesn't do is a smart resource utilization:
Harbor, in fact, during NS is deletion, it checks if any related VNF remains
orphan (which means without any NS using it). In that case the VNF will enter in
a state of pruning: after five minutes, if the VNF has not be reutilized by any
other NS it will be deleted. This mechanism assure faster deployments in
environments where NSs are continuously taken up and down.

@@

\subsubsection{Docker Swarm} Introduced in ??\todo{Find Docker Swarm date of
birth}, Docker Swarm allows multiple Docker nodes to cluster together and be
seen as one logical unit. This layer completely makes the underlying
infrastructure transparent: data management, as network one, are totaly managed
by Docker. Recently, Docker-compose support has been introduced, making this
one-node tool available for clustered systems. At the end of the day, on one
hand Docker Swarm provides an easy way to set up a cluster system with all the
tools configured out-of-the-box, without the necessity to set networking
configurations or installing ad-hoc storage solutions. On the other hand,
though, it doesn't have all the personalization options that Kuberentes offers,
thus making the product less flexible. This foundamental characteristic,
although, makes the two solutions have different use cases leading to different
market needs. \todo{Add Docker Swarm}

\subsubsection{Docker-compose} As briefly discussed above, Docker-compose is a tool
that allows services orchestration. It automates most of the tasks that should
be performed by hand when launching one or multiple docker containers. It's
particulary useful when more continers have to interact together,
because\todo{Write down docker-compose functionalities and describe the product
  a little bit} all the services rules are described in a simple YAML file. With
the birth of Docker Swarm, work has started to port this tool to the Swarm
framework. At the time of this writing, the procedure to port a Docker-compose
configuration in Docker Swarm is still not completely transparent, and it
requires a sort of compilation, where Docker-compose bundles all the necessaries
resources into a binary file that Docker Swarm will use to allocate the
necessary resources.
